%&latex                                                          
% Copyright 2011 Ruslan Kiyanchuk (c) <ruslan.kiyanchuk@gmail.com>
%/
\Chapter{INTRODUCTION}
\label{sec:intro}

Symmetric cryptographic transformations are known to be the only effective method
of providing data confidentiality and integrity in all fields of communication
technologies~\cite{moldovyan2007innovative}. They need to be not only
cryptographically strong, but also have high performance and low resources
consumption to satisfy modern needs for securing information. Consequently,
robust requirements on cryptographic security, lightweight implementation and
performance are entrusted to such transformations.

Symmetric ciphers came through a long history of development and improvement
from the most primitive schemes based on symbols substitution and disk
encryptors to advanced mathematical algorithms following Kerckhoffs'
principle~\cite{kahn1996codebreakers}.
A tremendous contribution to enciphering theory has been done by Claude
Shannon's work~\cite{shannon:secrecy} back in 1949. He introduced the
fundamentals of information theory and made it possible to evaluate and
mathematically prove cipher security. Ubiquitous computerization, mass
deployment of pervasive devices and extensive Internet access caused
cryptography to find comprehensive applications in information systems. Despite
the advanced mathematics behind modern cryptoalgorithms, real operating
security systems often have weaknesses due to incorrect usage or implementation
errors.

Security of mobile communication systems fell far behind from what was
state-of-the-art in modern cryptography. The A5/1 cipher used in GSM standard
for over 10 years can be broken within seconds using a combined distributed
rainbow table code book to decrypt GSM voice calls and text
messages~\cite{secproject}.
Communication over satellite phones has also been shown to be insecure after
reverse engineering the proprietary ciphers \mbox{GMR-1} and \mbox{GMR-2}.
\mbox{GMR-1} is a variant of A5/2 cipher (which is prohibited for
implementation in mobile phones as of July 2007) and is vulnerable to a known
ciphertext-only attack with an average case complexity of
$2^{32}$~\cite{3gpp:a52:2007}.
\mbox{GMR-2} is an original cipher, but its session key can be recovered with
65 bytes of keystream at a moderate computational
complexity~\cite{kiyanchuk:zuc}. 

The need of deep analysis and public evaluation of cryptographic algorithms
before deploying them into real systems is obvious. Several ciphers are
considered for becoming worldwide standards in the field of providing data
confidentiality at the moment. 

PRESENT is a lightweight block cipher published
as an ISO standard in 2012~\cite{isoiec-29192}. While being designed for
providing moderate security level it is not yet clear if the design of the cipher is
optimal for lightweight cryptography purposes. 

ZUC is a newly developed
Chinese stream cipher recommended for use in 3GPP Long Term Evolution (LTE)
mobile communications standard and going through public evaluation since
2011~\cite{3gpp:eea3_doc4}. After discovering few weaknesses some nontrivial
changes had been made to the cipher which is now exposed to the second
iteration of public evaluation\cite{3gpp:eea3_doc2}.

GOST~28147-89 is a legacy cipher that has been a subject to cryptanalysis
for more than 20 years. 
Despite its wide usage in Ukraine and
other CIS countries since the publication in 1990, the cipher has been proposed for
international standardization only in 2010, but hasn't been
accepted however~\cite{isoiec-18033}.
Therefore a detailed security evaluation and properties analysis of these
ciphers are needed before their pervasive deployment into security systems.

\labourprotection{
    Chapter~\ref{sec:labour} analyses PC users working conditions and
    their compliance with normative documents on safety engineering  and
    sanitation. For retrieving and evaluating the influence of possible dangerous
    or harmful production factors an interaction system
    ``Human--Machine--Environment'' (HME) is developed. Safety measures are
    developed as the result of such system analysis.
}
